### 2025-04-12 multiple-regression.qmd
20250411 - clean up

Here is the VIF from our earlier model:

@@

bayesianMultipleRegressionModel <- brm(
  formula = fantasyPoints_transformed ~ age + height + weight + I(log(target_share + 1)),
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  family = gaussian()
)

summary(bayesianMultipleRegressionModel)
```

>>>>

Here are the VIFs from our earlier model:

@@

bayesianMultipleRegressionModel <- brm(
  formula = fantasyPoints_transformed ~ age + height + weight + I(log(target_share + 1)),
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  family = gaussian()
)
```

```{r}
summary(bayesianMultipleRegressionModel)
```
